\documentclass{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{tgschola} % or any other font package you like

\newcommand{\soptitle}{Statement of Purpose}
\newcommand{\yourname}{Jimmy Lin}
\newcommand{\youremail}{jimmylin@utexas.edu}
\newcommand{\yourweb}{https://cs.utexas.edu/~jimmylin}

\usepackage[
  colorlinks,
  breaklinks,
  pdftitle={\yourname - \soptitle},
  pdfauthor={\yourname},
  unicode
]{hyperref}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{%
  \footnotesize\sffamily
  \yourname\quad
  web: \textcolor{blue}{\url{\yourweb}}\quad
  \textcolor{blue}{\url{\youremail}}}

\newcommand{\statement}[1]{\par\medskip
  \underline{\textcolor{blue}{\textbf{#1:}}}\space
}
\begin{document}

\begin{center}\LARGE\soptitle\\
\large of \yourname\ (CS Ph.D applicant for Fall--2015)
\end{center}

\hrule
\vspace{1pt}
\hrule height 1pt

\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 1 Describe your research interest
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
My research interest lies 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 2(a) Describe your Project A
% Describe some research projects that you worked on. What was the problem you
% were trying to solve? Why was it important? What approaches did you try? What
% did you learn? It’s fine to say that you were unable to fully solve your
% problem.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% introduction
The most significant research project in my investigative study in the field
of machine learning was \textit{Convex Optimization on Hard Clustering and
    Hierarchical Dirichilet Process}.
% how do you do your project
The partner I coordinated with for this research project was Ian Yen, an Ph.D
student supervised by Prof. Pradeep Ravikumar and Prof. Inderjit Dhillon.
% Aim of this project
This project, based on examplar-based model, aimed at developing efficient
algorithm with optimality guarantee on hard clustering problem(DP model) and 
(HDP model).
% Brief description of achievements and development process
Our approaches employed ADMM technique and obtain decent achievement on hard
clustering problem in various datasets.
After reaching desired consequence on clustering problem, we figured out that
it could be a decent breakthrough if we apply this framework on the
topic-model problem, whose essential goal was to cluster bag of words within
collections of documents. 
We designed objective function under our framework and corresponding computing
routines with both optimality guarantee and significantly refined
functionality.  The theory looked perfectly good but we failed to implement the
computaion due to incompatibility between our algorithm and the
objective component contributing to functionality augmentation.
After trial on theoretical debugging, we had to, with slight frustration, give
up the tempting functionality augmentation for topic model and derived an
efficient algorithm that seeks optimality of HDP model with guarantee.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 2(b) Describe your Project B
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Job Analytics was the project through which I made the first touch to
CS research with rigorous mathematics. The initial idea of
matching jobs to people in an intelligent way came from Prof. Pradeep Ravikumar.
This is 

Realize that excellent mastery of mathematics does matter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 2(c) Describe your Project C
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Another research project taken PHD program.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 3 Tell us why you feel you need a Ph.D..
% Look back to section 2 and explain what in there appealed to you.
% why is it consistent with your long-term goal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Why do you need a Ph.D.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section 4 Tell us why you want to come to CMU.
% Whom might you like to work with? What papers have you looked at from CMU
% that you enjoyed reading? Why is CMU the right place for you?
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% external 
Before summer of 2014, my perception towards Carnegie Mellon University was
the top in the area of computer science. 
% experience of MLSS
My personal feeling that Carnegie Mellon University was beta version of
beloved Australian National University, a place giving high respects to the
CMU.
% mention of my supervisor Pradeep 
My honor thesis supervisor Prof. Pradeep Ravikumar had his doctoral career in
CMU. He treated us as an individual researcher and discussed details with us.
% mention of Alex Smola

\end{document}
