%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  THIS TEX FILE IS TO GENERATE PDF FILE FOR 
%%% 
%%%  COPYRIGHT (C) JIMMY LIN, 2013, UT AUSTIN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  PACKAGES USED IN THIS TEX SOURCE FILE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{geometry,amsthm,amsmath,graphicx,fancyheadings,fancybox}
\usepackage{tikz}
\usepackage[colorlinks,
            linkcolor=blue,
            anchorcolor=red,
            citecolor=green
            ]{hyperref}
\usepackage{/Users/JimmyLin/workspace/latexTemplate/UTA_CS/JS}
\usepackage{/Users/JimmyLin/workspace/latexTemplate/UTA_CS/JSASGN}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% MACROS CONTAINING THE FILE INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\COURSE}{CS331 Algorithm}
\renewcommand{\LECTURER}{Greg Plexton}
\renewcommand{\TUTOR}{Chunzhi Zhu}
\renewcommand{\TASK}{Assignment 05}
\renewcommand{\RELEASEDATE}{March. 31 2014}
\renewcommand{\DUEDATE}{April. 9 2014}
\renewcommand{\TIMECONSUME}{15 hours}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% DOCUMENTATION STARTS FROM HERE 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TITLE PAGE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
    \maketitle
\end{titlepage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CONTENT PAGE: TABLEOFCONTENTS, LISTOFTABLES, LIST OF FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\contentsname}{Contents}
\begin{center} 
    \tableofcontents 
\end{center}
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% GENERAL DOCUMENTATION BEGINS 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\wm}[1]{\ensuremath{w(M_{#1})}}
\newcommand{\wmp}[1]{\ensuremath{w(M'_{#1})}}
\newcommand{\wmi}{\ensuremath{w(M_i)}}
\newcommand{\wmip}{\ensuremath{w(M'_i)}}
\newcommand{\constantTime}{\ensuremath{\mathcal{O}(1)}}
\newcommand{\linearTime}{\ensuremath{\mathcal{O}(n)}}
\newcommand{\lbw}[1]{\ensuremath{a_{#1} q_{#1} + b_{#1}}}  %% linear bid weight
\newcommand{\sbw}[1]{\ensuremath{m_{#1}}}

\newcommand{\Pt}{\ensuremath{P(G, M, p)}}
\newcommand{\Pzero}{\ensuremath{P_0(G, p)}}
\newcommand{\Pone}{\ensuremath{P_1(G, M, p)}}
\newcommand{\Ptwo}{\ensuremath{P_2(G, M, p)}}


\section{Exercise 2}
\ovalbox{
\begin{minipage}{15cm} 
Consider an iteration of Algorithm A on a configuration $G = (U,V,E)$ that
increments the price of an item due to a violation of Stability Condition 2.
Assume that the MCM M of G associated with this execution of Algorithm A is an
MWMCM of $G$. Let $p (resp., p_0)$ denote the price vector of G maintained by
Algorithm A just before (resp., after) this iteration. Prove that if $P_0(G,p)$
holds, then so does $P_0(G,p_0)$. Hint: Make use of Lemma 1 of Assignment 4.
\end{minipage} } \\

In order to prove that if $\Pzero$ holds, then $P_0{G, p'}$ holds after one
iteration of algorithm A, we should prove it for all three possible violation
cases of algorithm A.

\begin{proof}[Stability Condition 1 is violated]
    In this case, the algorithm A will halts "unsuccessfully". Hence, there is
    no change for price vector after the iteration. That is, we have $p = p'$.
    And obviously, it is true that if $\Pzero$ holds, then $P_0(G, p')$ holds.
\end{proof}

\begin{proof}[Stability Condition 2 is violated]
    Since the violation of stability condition 2 causes the iteration of
    algorithm A, it is true that 
    
    \begin{align}
        \exists u,\ (u, v) \in M,\ (u, v^*) \in E,\ s.t.\ 
        w(u, v) - p_{v} < w(u, v^*) - p_{v^*}
    \end{align}
    
    Let us instantiate the $v$ to $v_0$ and $v^*$ to $v_1$, and have
    
    \begin{align}
        w(u, v_0) - p_{v_0} < w(u, v_1) - p_{v_1}
    \end{align}

    In this case, the $p'_{v_1}$ will increments by 1, it is true that
    \begin{align}
        w(u, v_0) - p_{v_0} \leq w(u, v_1) - p'_{v_1}
    \end{align}

    that is,

    \begin{align} \label{ex2:p_v_1leqbala}
         p'_{v_1} \leq w(u, v_1) - w(u, v_0) + p_{v_0}
    \end{align}

    For the stable price vector $q$, according the stability condition 2, we
    have 

    \begin{align}
        \forall v^{*},\ w(u, v^{*}) - q_{v^{*}} \leq w(u, v_0) - q_{v_0}    
    \end{align}

    Let us instantiate the $v^{*}$ to $v_1$ and have

    \begin{align}
        w(u, v_1) - q_{v_1} \leq w(u, v_0) - q_{v_0}
    \end{align}

    That is, 

    \begin{align}
        w(u, v_1) - w(u, v_0) + q_{v_0} \leq q_{v_1}
    \end{align}

    Since $p_{v_0} \leq q_{v_0}$ holds,

    \begin{align}
        w(u, v_1) - w(u, v_0) + p_{v_0} \leq q_{v_1}
    \end{align}

    Combined with \eqref{ex2:p_v_1leqbala}, we have

    \begin{align}
        p'_{v_1} \leq q_{v_1}
    \end{align}

    Since $p'_{v_1}$ is the only item whose price is changed in this
    iteration, $\forall v \neq v_1,\ p'_{v} \leq q_{v_1}$ holds. Hence, we can
    conclude that after the iteration of algorithm A with the cause of
    stability violation 2, Predicate 0 still holds.
    That is, $ \Pzero \Rightarrow P_0(G, p') $ holds if one iteration is
    caused by stability violation 2.

\end{proof}

\begin{proof}[Stability Condition 3 is violated]

    In the violation of stability condition 3, we have

    \begin{align}
        \exists v^{*},\ (u^{*}, v^{*}) \in E,\ u^{*} is unmatched in M,\ p_{v^{*}} < w(u^{*}, v^{*})
    \end{align}

    Let $u_0$ to be a unmatched bid in $M$, and $(u_0, v_0) \in E$. 
    Hence, we can instantiate $v^{*}$ to $v_0$, and $u^{*}$ to $u_0$

    \begin{align}
        (u_0, v_0) \in E,\ p_{v_0} < w(u_0, v_0)
    \end{align}
    
    Since the algorithm A in this case will increment $p_{v_0}$ by one and other
    price component remains unchanged, we have

    \begin{align} \label{ex2:p3:babbaa}
        p_{v_0} \leq w(u, v_0)
    \end{align}

    Since M is already MWMCM, and $q$ is stable price vector, then $(M, q)$ is
    stable solution. According to the third property of stable solution, we
    have

    \begin{align}
        \forall u^{*} \in U,\ u^{*} is unmatched in M,\ w(u^{*}, v_0) \leq q_{v_0}
    \end{align}

    We instantiate $u^{*}$ to $u_0$, which is reasonable because $u_0$ Then we have

    \begin{align}
        w(u_0, v_0) \leq q_{v_0}
    \end{align}

    Combined with \eqref{ex2:p3:babbaa}, it is true that

    \begin{align}
        p_{v_0} \leq q_{v_0}
    \end{align}

    Since other price component does not vary at that iteration, we can
    conclude that $p \leq q$ holds in this case. That is, $ \Pzero \Rightarrow
    P_0(G, p') $ holds if one iteration is caused by stability violation 3.

\end{proof}

    Since one iteration in algorithm A will only be caused by one of three
    cases, and in all of these three cases, $ \Pzero \Rightarrow
    P_0(G, p') $ holds for that iteration, it can be concluded that if $\Pone$
    holds, then so does $P_1(G, M, p')$.

    \newpage
\section{Exercise 5}
\ovalbox{
\begin{minipage}{15cm}
    Consider an execution of Algorithm A on a configuration $G = (U,V,E)$.
    Assume that the associated MCM $M$ of $G$ is an MWMCM of $G$, and that the
    initial price vector $p$ for $G$ is such that $\Pt$ holds. Prove that
    Algorithm $A$ is guaranteed to halt successfully within a finite number of
    iterations. Hint: Make use of Lemma 3.
\end{minipage} } \\[0.5cm]

\begin{proof}[Proof by Contradiction]
    First assume that Algorithm A is {\bf not necessarily} guaranteed to halt
    successfully within a finite number of iterations. That is to say, it is
    possible for Algorithm A to unsuccessfully halt at certain iteration. Let
    us say the halting iteration to be iteration $k$. Since the algorithm A
    halts at iteration $k$, the only possibility comes from the violation of stability
    condition 1 for price vector $p$. That is,
    
    \begin{align}  \label{ex5:p1bab}
        \exists (u,v) \in M,\ w(u,v) < p_v
    \end{align}

    Let us see how the above formula contradicts the known condition $\Pt$.

    For an stable price vector $q$, and an MWMCM $M$, we have
    \begin{align} \label{ex5:forfixedp}
        \forall v,\ q_v \leq w(u,v)
    \end{align}

    Combined with \eqref{ex5:p1bab}, it can be easily seen that 
    \begin{align} \label{ex5:wederive}
        \exists (u,v) \in M,\ q_v < p_v
    \end{align}

    However, we already know that $\Pt$ holds and if $\Pt$, then $\Pone$ must
    hold.  Hence, $\Pone$ holds. That is,

    \begin{align} \label{ex5:tocontra}
        \forall v,\ p_v < q_v
    \end{align}
    where $q$ can be arbitrary stable price vector, but here we just
    instantiate it to be the same stable price vector in \eqref{ex5:forfixedp} for convenience.

    Now we can see that there is a contradiction between \eqref{ex5:wederive}
    and \eqref{ex5:tocontra}. Hence, we should negate the initial assumption
    and conclude that Algorithm $A$ is guaranteed to halt successfully within
    a finite number of iterations. 

\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% General Documentation ends
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
